Resolvable Ambiguity

### 2019-07-11 paper/paper.tex
Added missing reference

Silver \cite{vanwykSilverExtensibleAttribute2010}, a system for defining extensible languages using attribute grammars, and its associated parser Copper \cite{} have a ``Modular Well-Definedness Analysis'' \cite{kaminskiModularWellDefinednessAnalysis2013}, with which extension language developers can check that their extension will compose well with other extensions, without any knowledge of any particular other extension. For this paper, only the syntactic component \cite{schwerdfegerVerifiableCompositionDeterministic2009} of this analysis is relevant. This analysis guarantees that the composition of a base language and any number of extensions that have passed it will compose to a grammar in LALR(1). This is a far more restricted class of languages than unambiguous languages, not to mention resolvably ambiguous languages, and thus places far more restrictions on language designers than our approach.

>>>>

Silver \cite{vanwykSilverExtensibleAttribute2010}, a system for defining extensible languages using attribute grammars, and its associated parser Copper \cite{vanwykCopper2007} have a ``Modular Well-Definedness Analysis'' \cite{kaminskiModularWellDefinednessAnalysis2013}, with which extension language developers can check that their extension will compose well with other extensions, without any knowledge of any particular other extension. For this paper, only the syntactic component \cite{schwerdfegerVerifiableCompositionDeterministic2009} of this analysis is relevant. This analysis guarantees that the composition of a base language and any number of extensions that have passed it will compose to a grammar in LALR(1). This is a far more restricted class of languages than unambiguous languages, not to mention resolvably ambiguous languages, and thus places far more restrictions on language designers than our approach.
